\thetitle

### 2020-12-04 sun_phases/spin_qudit_tomo.tex
minor change to wording in paragraph about Husimi distribution

As a special case, the phase-space representation $\rho^{\t{PS}}$ of a qudit state $\rho$ is commonly known as its Husimi distribution.
Performing tomography on an unknown qudit state $\rho$ is therefore equivalent to reconstructing the unknown distribution $\rho^{\t{PS}}$ on the sphere.
In principle, the representation $\rho^{\t{PS}}$ of a finite-dimensional qudit state $\rho$ can be reconstructed from the values $\rho^{\t{PS}}\p{\v v}=\bk{s_{\v v}|\rho|s_{\v v}}$ at a finite number of points $\v v$ on the sphere.
In practice, the value $\bk{s_{\v v}|\rho|s_{\v v}}$ is determined by measuring spin projection along $\v v$, which also provides measurement data on all spin projections $\bk{\mu_{\v v}|\rho|\mu_{\v v}}$ with $\mu\in\set{s,s-1,\cdots,-s}$ and $\ket{\mu_{\v v}}\equiv R\p{\v v}\ket{\mu}$; one would like to make use of this additional data as well.
We clarify the connection between the quantum problem of reconstructing $\rho$ from spin projection measurements and the classical problem of reconstructing $\rho^{\t{PS}}$ from its values $\rho^{\t{PS}}\p{\v v}$ in the following section.
In addition to providing a new perspective on the problem of spin qudit tomography, the connection will allow us to place upper bounds on the minimal number of measurement axes $\v v$ necessary for full recovery of an unknown state.

>>>>

As a special case, the phase-space representation $\rho^{\t{PS}}$ of a qudit state $\rho$ is commonly known as its Husimi distribution.
Performing tomography on an unknown qudit state $\rho$ is therefore equivalent to reconstructing the unknown distribution $\rho^{\t{PS}}$ on the sphere.
In principle, the representation $\rho^{\t{PS}}$ of a finite-dimensional qudit state $\rho$ can be reconstructed from the values $\rho^{\t{PS}}\p{\v v}=\bk{s_{\v v}|\rho|s_{\v v}}$ at a finite number of points $\v v$.
In practice, the value $\bk{s_{\v v}|\rho|s_{\v v}}$ is determined by measuring spin projection along $\v v$, which also provides measurement data on all spin projections $\bk{\mu_{\v v}|\rho|\mu_{\v v}}$ with $\mu\in\set{s,s-1,\cdots,-s}$ and $\ket{\mu_{\v v}}\equiv R\p{\v v}\ket{\mu}$; one would like to make use of this additional data as well.
We clarify the connection between the quantum problem of reconstructing $\rho$ from spin projection measurements and the classical problem of reconstructing $\rho^{\t{PS}}$ from its values $\rho^{\t{PS}}\p{\v v}$ in the following section.
In addition to providing a new perspective on the problem of spin qudit tomography, this connection will allow us to place upper bounds on the minimal number of measurement axes $\v v$ necessary for full recovery of an unknown state.
